Face Attractiveness and the Sense of Reality

### 2022-08-25 analysis.Rmd
remove rawdata

```{r message=FALSE, warning=FALSE}
df |>
  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
    summarize(Real = mean(Real)) |>
    ungroup() |>
    arrange(Real) |>
    pull(Participant))) |>
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(-100, 100),
    expand = c(0.01, 0.01),
    breaks = c(-100, 0, 100),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  geom_point() +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted))
```

>>>>

```{r message=FALSE, warning=FALSE}
df |>
  mutate(Participant = fct_relevel(Participant, group_by(df, Participant) |>
    summarize(Real = mean(Real)) |>
    ungroup() |>
    arrange(Real) |>
    pull(Participant))) |>
  ggplot(aes(x = Real, y = Participant, fill = Participant)) +
  ggdist::stat_slab(scale = 2, slab_alpha = 0.9) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  scale_y_discrete(expand = c(1, 1)) +
  scale_x_continuous(
    limits = c(-1, 1),
    expand = c(0.01, 0.01),
    breaks = c(-1, 0, 1),
    label = c("Fake", "0", "Real")
  ) +
  scale_fill_viridis_d() +
  labs(x = "Simulation Monitoring", y = "Participants", title = "Distribution of Reality Judgments") +
  guides(fill = "none") +
  see::theme_modern() +
  theme(
    axis.text.y = element_blank(),
    plot.title = element_text(face = "bold", hjust = 0.5)
  )
```

@@

df |> 
  ggplot(aes(x = Attractive, y = Real)) +
  ggside::geom_xsidedensity(fill = "#F44336", color="white") +
  ggside::geom_ysidedensity(fill = "#9C27B0", color="white") +
  ggside::theme_ggside_void() +
  geom_hline(yintercept = 0, linetype = "dotted") +
  geom_point() +
  geom_ribbon(data = pred, aes(y = Predicted, ymin = CI_low, ymax = CI_high), alpha = 0.5) +
  geom_line(data = pred, aes(y = Predicted))
```
